Data Pre-Processing

### 2021-05-05 AST-Framing-Ontario/Data Pre-Processesing.rmd
CorpusKey before stopwords

@@

corpusNum <- c(corpusNum, paste(m))

@@

Creating Term-Document Matrix and Document-Term Matrix with the fully cleaned corpora.
```{r}
# n - number of corpora
n <- 4
for (i in seq(1, n, 1))
{
tempCorpus <-  eval(parse(text = paste("corpus", i, sep = "")))
TDM <- TermDocumentMatrix(tempCorpus)
DTM <- DocumentTermMatrix(tempCorpus)
matrix1 <- as.matrix(TDM)
matrix2 <- as.matrix(DTM)

@@

```{r}
# n - number of corpora
n <- 4

for (i in seq(1, n, 1))
{
  tempDF <- eval(parse(text = paste("cleanTextDF", i, sep = "")))
  it_train = itoken(tempDF$text, progressbar = FALSE)
  assign(paste("vocab", i, sep= ""), create_vocabulary(it_train))
  tempVocab <- create_vocabulary(it_train)
  assign(paste("vocab", i, sep= ""), prune_vocabulary(tempVocab, term_count_min = 5))
}

>>>>

'n' represents the number of subfolders and subsequently corpora that you intent the produce. 'corpusKey' will indicate the numbering convention of the corpora and analysis in subsequent code. 
```{r}
# n - number of corpora
n <- 4
corpusNum <- seq(1, n, 1)
corpusKey <- data.frame(corpusNum, subFolders)
```

@@

@@

Creating Term-Document Matrix and Document-Term Matrix with the fully cleaned corpora.
```{r}
for (i in seq(1, n, 1))
{
tempCorpus <-  eval(parse(text = paste("corpus", i, sep = "")))
TDM <- TermDocumentMatrix(tempCorpus)
DTM <- DocumentTermMatrix(tempCorpus)
matrix1 <- as.matrix(TDM)
matrix2 <- as.matrix(DTM)

@@

```{r}
for (i in seq(1, n, 1))
{
  tempDF <- eval(parse(text = paste("cleanTextDF", i, sep = "")))
  it_train = itoken(tempDF$text, progressbar = FALSE)
  assign(paste("vocab", i, sep= ""), create_vocabulary(it_train))
  tempVocab <- create_vocabulary(it_train)
  assign(paste("vocab", i, sep= ""), prune_vocabulary(tempVocab, term_count_min = 5))
}
